
####  PREDICTION MODEL ###################################################


title: "Temporary series: TFM sales forecast"
author: "Eduardo Colmenares"
Input:
 Historical data and diferents information to predict the future production
     File Prod_factVT2.csv.csv -  Historical Data
     File Service_type.csv - Summarized services 
     File DIAS LAB.csv - Labor days 

output:
  # Predictions of future production 



INSTALL PACKAGES 

```{r install, include=FALSE}

package.names <- c("knitr",
                   "ggplot2",
                   "patchwork",
                   "tidyverse",
                   "dslabs",
                   "lubridate",
                   "purrr",
                   "pdftools",
                   "fracdiff",
                   "fpp2", 
                   "tseries", 
                   "TTR", 
                   "seasonal",
                   "zoo",
                   "xts",
                   "greybox",
                   "smooth" ,
                   "Metrics",
                   "gridExtra",
                   "prophet"
                   )

for (package.name in package.names){
  if(!require(package.name, character.only = T)){install.packages(package.name, type = "both")}
}

all.packages <- c(package.names)
```

```{r libraries, include=FALSE}
for (package.name in all.packages){
  library(package.name, character.only = T)
}
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## READ FILES  

Read CSV files 
   Prod_factVT2.csv - Historical data of the services by clients from Jan 2017
   Service_type.csv - Summarize service information in 5 categories (PREM, 19H, ECOM, PPACK, OT, I)
   DIAS LAB.csv - Labor days of Spain and Portugal 

```{r}
df.services = read.csv2("Prod_factVT2.csv")
df.servicestype = read.csv2("Service_type.csv")
df.lab = read.csv2("DIAS LAB.csv")
```


## MERGE DATAFRAMES 

    Historical data with the services summarized information 

```{r}
df.services$Date <- as.Date (df.services$Date, format = "%d/%m/%Y") 
df.services$shipments <- as.integer (df.services$shipments) 
df.services <- merge(
  x = df.services,
  y = df.servicestype,
  by = "Service",
  all.x = TRUE
)
df.lab$Date <- as.Date (df.lab$Date, format = "%d/%m/%Y") 
df.lab$date <- df.lab$Date - days(as.integer(format(df.lab$Date, "%d"))) + 1
```

```{r}
write_excel_csv2(df.services, file = "alldataEXCEL.csv")
```


# DATA ANALYSYS OF THE INFORMATION 

Filter services information by country  

```{r}

#ESP
df.tmservicesESP = df.services %>% 
           filter(Country == "ESP") %>%
           mutate(Date = as.Date(Date)) %>% 
           group_by(Date) %>% 
           summarize(total_sum = sum(shipments))

df.tmservicesESP <- merge(
           x = df.tmservicesESP,
           y = df.lab,
           by = "Date",
           all.x = TRUE)

df.tmservicesESP$total_shipments = df.tmservicesESP$total_sum / df.tmservicesESP$DLABESP


#POR
df.tmservicesPOR = df.services %>% 
           filter(Country == "POR") %>%
           mutate(Date = as.Date(Date)) %>% 
           group_by(Date) %>% 
           summarize(total_sum = sum(shipments))

df.tmservicesPOR <- merge(
           x = df.tmservicesPOR,
           y = df.lab,
           by = "Date",
           all.x = TRUE)

df.tmservicesPOR$total_shipments = df.tmservicesPOR$total_sum / df.tmservicesPOR$DLABPOR

#head(df.tmservicesESP)
#head(df.tmservicesPOR)

```


Filter services by type of service  

PREMIUM 
```{r}
#ESP AND SERV PREM
df.tmservicesESPPREM = df.services %>% 
           filter(Country == "ESP") %>%
           filter(Serv_cod == "PREM") %>%
           mutate(Date = as.Date(Date)) %>% 
           group_by(Date) %>% 
           summarize(total_sum = sum(shipments))
df.tmservicesESPPREM <- merge(
           x = df.tmservicesESPPREM,
           y = df.lab,
           by = "Date",
           all.x = TRUE)
df.tmservicesESPPREM$total_shipments = df.tmservicesESPPREM$total_sum / df.tmservicesESPPREM$DLABESP

#POR AND SERV PREM
df.tmservicesPORPREM = df.services %>% 
           filter(Country == "POR") %>%
           filter(Serv_cod == "PREM") %>%
           mutate(Date = as.Date(Date)) %>% 
           group_by(Date) %>% 
           summarize(total_sum = sum(shipments))
df.tmservicesPORPREM <- merge(
           x = df.tmservicesPORPREM,
           y = df.lab,
           by = "Date",
           all.x = TRUE)
df.tmservicesPORPREM$total_shipments = df.tmservicesPORPREM$total_sum / df.tmservicesPORPREM$DLABPOR
```

19H 
```{r}
#ESP AND SERV 19H
df.tmservicesESP19H = df.services %>% 
           filter(Country == "ESP") %>%
           filter(Serv_cod == "19H") %>%
           mutate(Date = as.Date(Date)) %>% 
           group_by(Date) %>% 
           summarize(total_sum = sum(shipments))
df.tmservicesESP19H <- merge(
           x = df.tmservicesESP19H,
           y = df.lab,
           by = "Date",
           all.x = TRUE)
df.tmservicesESP19H$total_shipments = df.tmservicesESP19H$total_sum / df.tmservicesESP19H$DLABESP
#POR AND SERV 19H
df.tmservicesPOR19H = df.services %>% 
           filter(Country == "POR") %>%
           filter(Serv_cod == "19H") %>%
           mutate(Date = as.Date(Date)) %>% 
           group_by(Date) %>% 
           summarize(total_sum = sum(shipments))
df.tmservicesPOR19H <- merge(
           x = df.tmservicesPOR19H,
           y = df.lab,
           by = "Date",
           all.x = TRUE)
df.tmservicesPOR19H$total_shipments = df.tmservicesPOR19H$total_sum / df.tmservicesPOR19H$DLABPOR
```

ECOM 
```{r}
#ESP AND SERV ECOM
df.tmservicesESPECOM = df.services %>% 
           filter(Country == "ESP") %>%
           filter(Serv_cod == "ECOM") %>%
           mutate(Date = as.Date(Date)) %>% 
           group_by(Date) %>% 
           summarize(total_sum = sum(shipments))
df.tmservicesESPECOM <- merge(
           x = df.tmservicesESPECOM,
           y = df.lab,
           by = "Date",
           all.x = TRUE)
df.tmservicesESPECOM$total_shipments = df.tmservicesESPECOM$total_sum / df.tmservicesESPECOM$DLABESP
#POR AND SERV ECOM
df.tmservicesPORECOM = df.services %>% 
           filter(Country == "POR") %>%
           filter(Serv_cod == "ECOM") %>%
           mutate(Date = as.Date(Date)) %>% 
           group_by(Date) %>% 
           summarize(total_sum = sum(shipments))
df.tmservicesPORECOM <- merge(
           x = df.tmservicesPORECOM,
           y = df.lab,
           by = "Date",
           all.x = TRUE)
df.tmservicesPORECOM$total_shipments = df.tmservicesPORECOM$total_sum / df.tmservicesPORECOM$DLABPOR
```

PPACK 
```{r}
#ESP AND SERV PPACK
df.tmservicesESPPPACK = df.services %>% 
           filter(Country == "ESP") %>%
           filter(Serv_cod == "PPACK") %>%
           mutate(Date = as.Date(Date)) %>% 
           group_by(Date) %>% 
           summarize(total_sum = sum(shipments))
df.tmservicesESPPPACK <- merge(
           x = df.tmservicesESPPPACK,
           y = df.lab,
           by = "Date",
           all.x = TRUE)
df.tmservicesESPPPACK$total_shipments = df.tmservicesESPPPACK$total_sum / df.tmservicesESPPPACK$DLABESP
#POR AND SERV PPACK
df.tmservicesPORPPACK = df.services %>% 
           filter(Country == "POR") %>%
           filter(Serv_cod == "PPACK") %>%
           mutate(Date = as.Date(Date)) %>% 
           group_by(Date) %>% 
           summarize(total_sum = sum(shipments))
df.tmservicesPORPPACK <- merge(
           x = df.tmservicesPORPPACK,
           y = df.lab,
           by = "Date",
           all.x = TRUE)
df.tmservicesPORPPACK$total_shipments = df.tmservicesPORPPACK$total_sum / df.tmservicesPORPPACK$DLABPOR
```

OT 
```{r}
#ESP AND SERV PPACK
df.tmservicesESPOT = df.services %>% 
           filter(Country == "ESP") %>%
           filter(Serv_cod == "OT") %>%
           mutate(Date = as.Date(Date)) %>% 
           group_by(Date) %>% 
           summarize(total_sum = sum(shipments))
df.tmservicesESPOT <- merge(
           x = df.tmservicesESPOT,
           y = df.lab,
           by = "Date",
           all.x = TRUE)
df.tmservicesESPOT$total_shipments = df.tmservicesESPOT$total_sum / df.tmservicesESPOT$DLABESP
#POR AND SERV PPACK
df.tmservicesPOROT = df.services %>% 
           filter(Country == "POR") %>%
           filter(Serv_cod == "OT") %>%
           mutate(Date = as.Date(Date)) %>% 
           group_by(Date) %>% 
           summarize(total_sum = sum(shipments))
df.tmservicesPOROT <- merge(
           x = df.tmservicesPOROT,
           y = df.lab,
           by = "Date",
           all.x = TRUE)
df.tmservicesPOROT$total_shipments = df.tmservicesPOROT$total_sum / df.tmservicesPOROT$DLABPOR
```

I 
```{r}
#ESP AND SERV I
df.tmservicesESPI = df.services %>% 
           filter(Country == "ESP") %>%
           filter(Serv_cod == "I") %>%
           mutate(Date = as.Date(Date)) %>% 
           group_by(Date) %>% 
           summarize(total_sum = sum(shipments))
df.tmservicesESPI <- merge(
           x = df.tmservicesESPI,
           y = df.lab,
           by = "Date",
           all.x = TRUE)
df.tmservicesESPI$total_shipments = df.tmservicesESPI$total_sum / df.tmservicesESPI$DLABESP


#POR AND SERV PPACK
df.tmservicesPORI = df.services %>% 
           filter(Country == "POR") %>%
           filter(Serv_cod == "I") %>%
           mutate(Date = as.Date(Date)) %>% 
           group_by(Date) %>% 
           summarize(total_sum = sum(shipments))
df.tmservicesPORI <- merge(
           x = df.tmservicesPORI,
           y = df.lab,
           by = "Date",
           all.x = TRUE)
df.tmservicesPORI$total_shipments = df.tmservicesPORI$total_sum / df.tmservicesPORI$DLABPOR
```


Create timeseries and evaluate best forecast model 

COUNTRY 

SPAIN 
```{r}
# ts by country

serviceseriesESP <- ts(df.tmservicesESP$total_shipments, frequency=12, start = c(2017,1))
serviceseriesPOR <- ts(df.tmservicesPOR$total_shipments, frequency=12, start = c(2017,1))

```

FORECAST EVALUATION MODEL
```{r}
serviceseriesESP_train <- window(serviceseriesESP,
                                 start=start(serviceseriesESP), 
                                 end=end(serviceseriesESP)-c(1,0)) # - 1YEAR 

months.forecast <- 12
model_mean <- meanf(serviceseriesESP_train, lambda = "auto", h = months.forecast)
model_naive <- naive(serviceseriesESP_train, lambda = "auto", h = months.forecast)
model_snaive <- snaive(serviceseriesESP_train, lambda = "auto", h = months.forecast)
model_sma <- sma(serviceseriesESP_train, lambda = "auto") %>% forecast(h=months.forecast)
model_ets <- ets(serviceseriesESP_train, lambda = "auto") %>% forecast(h = months.forecast)
model_arima <- auto.arima(serviceseriesESP_train, lambda = "auto") %>% forecast(h = months.forecast)
autoplot(serviceseriesESP_train) +
  autolayer(model_mean, series=model_mean$method, alpha=0.9, PI=FALSE, size=1) + 
  autolayer(model_naive, series=model_naive$method, alpha=0.9, PI=FALSE, size=1) + 
  autolayer(model_snaive, series=model_snaive$method, alpha=0.9, PI=FALSE, size=1) + 
  autolayer(model_sma, series=model_sma$model$model, alpha=0.9, PI=FALSE, size=1) + 
  autolayer(model_ets, series=model_ets$method, alpha=0.9, PI=FALSE, size=1) + 
  autolayer(model_arima, series=model_arima$method, alpha=0.9, PI=FALSE, size=1)  +
  autolayer(serviceseriesESP, color=1, alpha=0.7)

```

ERRORS
```{r}
res <- data.frame(Mean=t(forecast::accuracy(model_mean, serviceseriesESP)),
           Naive=t(forecast::accuracy(model_naive, serviceseriesESP)),
           SNaive=t(forecast::accuracy(model_snaive, serviceseriesESP)),
           ETS=t(forecast::accuracy(model_ets, serviceseriesESP)),
           ARIMA=t(forecast::accuracy(model_arima, serviceseriesESP))) %>%
  rownames_to_column("Metric") %>%
  pivot_longer(cols=-Metric, names_sep = "\\.", names_to = c("Method","Set"), values_to = "Result")
ggplot(data = res %>% filter(Metric %in% c("RMSE","MAE","MAPE")), aes(x = Method, y = Result, fill = Method)) +
  geom_bar(stat = "identity", position="dodge") +  
  geom_point(colour="black",pch=21, size=2) + 
  scale_fill_discrete(name = "Modelos") +
  facet_wrap(~ Set + Metric, scales = "free", nrow = 2) + 
  theme(
      axis.text.x = element_blank(),
      axis.ticks.x = element_blank()
    )


```

---------------------------------------------------

PORTUGAL 
```{r}
# ts by country

serviceseriesESP <- ts(df.tmservicesESP$total_shipments, frequency=12, start = c(2017,1))
serviceseriesPOR <- ts(df.tmservicesPOR$total_shipments, frequency=12, start = c(2017,1))

```

FORECAST EVALUATION MODEL
```{r}
serviceseriesPOR_train <- window(serviceseriesPOR,
                                 start=start(serviceseriesPOR), 
                                 end=end(serviceseriesPOR)-c(1,0)) # - 1YEAR 

months.forecast <- 12
model_mean <- meanf(serviceseriesPOR_train, lambda = "auto", h = months.forecast)
model_naive <- naive(serviceseriesPOR_train, lambda = "auto", h = months.forecast)
model_snaive <- snaive(serviceseriesPOR_train, lambda = "auto", h = months.forecast)
model_sma <- sma(serviceseriesPOR_train, lambda = "auto") %>% forecast(h=months.forecast)
model_ets <- ets(serviceseriesPOR_train, lambda = "auto") %>% forecast(h = months.forecast)
model_arima <- auto.arima(serviceseriesPOR_train, lambda = "auto") %>% forecast(h = months.forecast)
autoplot(serviceseriesPOR_train) +
  autolayer(model_mean, series=model_mean$method, alpha=0.9, PI=FALSE, size=1) + 
  autolayer(model_naive, series=model_naive$method, alpha=0.9, PI=FALSE, size=1) + 
  autolayer(model_snaive, series=model_snaive$method, alpha=0.9, PI=FALSE, size=1) + 
  autolayer(model_sma, series=model_sma$model$model, alpha=0.9, PI=FALSE, size=1) + 
  autolayer(model_ets, series=model_ets$method, alpha=0.9, PI=FALSE, size=1) + 
  autolayer(model_arima, series=model_arima$method, alpha=0.9, PI=FALSE, size=1)  +
  autolayer(serviceseriesPOR, color=1, alpha=0.7)

```

ERRORS
```{r}
res <- data.frame(Mean=t(forecast::accuracy(model_mean, serviceseriesPOR)),
           Naive=t(forecast::accuracy(model_naive, serviceseriesPOR)),
           SNaive=t(forecast::accuracy(model_snaive, serviceseriesPOR)),
           ETS=t(forecast::accuracy(model_ets, serviceseriesPOR)),
           ARIMA=t(forecast::accuracy(model_arima, serviceseriesPOR))) %>%
  rownames_to_column("Metric") %>%
  pivot_longer(cols=-Metric, names_sep = "\\.", names_to = c("Method","Set"), values_to = "Result")
ggplot(data = res %>% filter(Metric %in% c("RMSE","MAE","MAPE")), aes(x = Method, y = Result, fill = Method)) +
  geom_bar(stat = "identity", position="dodge") +  
  geom_point(colour="black",pch=21, size=2) + 
  scale_fill_discrete(name = "Modelos") +
  facet_wrap(~ Set + Metric, scales = "free", nrow = 2) + 
  theme(
      axis.text.x = element_blank(),
      axis.ticks.x = element_blank()
    )


```




## FORECAST BY COUNTRY

```{r}
# ts by country

serviceseriesESP <- ts(df.tmservicesESP$total_shipments, frequency=12, start = c(2017,1))
serviceseriesPOR <- ts(df.tmservicesPOR$total_shipments, frequency=12, start = c(2017,1))

# forecast by country

months.forecast <- 17
#ESP
best_model_ESP <- ets(serviceseriesESP, lambda = "auto") %>% forecast(h = months.forecast)

predictionsESP <- predict(best_model_ESP, newdata = future_production)

df.predictions <- data.frame(date = as.Date(time(predictionsESP$mean)), meanpred_ESP = predictionsESP$mean)

df.predictionscountry <- rbind(df.predictions)
rm(df.predictions)

#POR
best_model_POR <- auto.arima(serviceseriesPOR, lambda = "auto") %>% forecast(h = months.forecast)

predictionsPOR <- predict(best_model_POR, newdata = future_production)

df.predictions <- data.frame(date = as.Date(time(predictionsPOR$mean)), meanpred_POR = predictionsPOR$mean)

df.predictionscountry <- merge(
           x = df.predictionscountry,
           y = df.predictions,
           by = "date",
           all.x = TRUE)

rm(df.predictions)

#forecast in months 
df.predictionscountry<- merge(
           x = df.predictionscountry,
           y = df.lab[c("date","DLABESP","DLABPOR")],
           by = "date",
           all.x = TRUE,
           )


df.predictionscountry$DLABESP = as.numeric(df.predictionscountry$DLABESP)
df.predictionscountry$DLABPOR = as.numeric(df.predictionscountry$DLABPOR)

df.predictionscountry$F_ESP = df.predictionscountry$meanpred_ESP * df.predictionscountry$DLABESP
df.predictionscountry$F_POR = df.predictionscountry$meanpred_POR * df.predictionscountry$DLABPOR

#head (df.predictionscountry)
write.csv(df.predictionscountry, file = "predictionsCOUNTRY.csv")
```


## FORECAST BY TYPE OF SERVICE

```{r}
# ts by SERVICE
#ESP
serviceseriesESPPREM <- ts(df.tmservicesESPPREM$total_shipments, frequency=12, start = c(2017,1))
serviceseriesESP19H <- ts(df.tmservicesESP19H$total_shipments, frequency=12, start = c(2017,1))
serviceseriesESPECOM <- ts(df.tmservicesESPECOM$total_shipments, frequency=12, start = c(2017,1))
serviceseriesESPPPACK <- ts(df.tmservicesESPPPACK$total_shipments, frequency=12, start = c(2017,1))
serviceseriesESPOT <- ts(df.tmservicesESPOT$total_shipments, frequency=12, start = c(2017,1))
serviceseriesESPI <- ts(df.tmservicesESPI$total_shipments, frequency=12, start = c(2017,1))
#POR
serviceseriesPORPREM <- ts(df.tmservicesPORPREM$total_shipments, frequency=12, start = c(2017,1))
serviceseriesPOR19H <- ts(df.tmservicesPOR19H$total_shipments, frequency=12, start = c(2017,1))
serviceseriesPORECOM <- ts(df.tmservicesPORECOM$total_shipments, frequency=12, start = c(2017,1))
serviceseriesPORPPACK <- ts(df.tmservicesPORPPACK$total_shipments, frequency=12, start = c(2017,1))
serviceseriesPOROT <- ts(df.tmservicesPOROT$total_shipments, frequency=12, start = c(2017,1))
serviceseriesPORI <- ts(df.tmservicesPORI$total_shipments, frequency=12, start = c(2017,1))

# forecast by SERVICE
months.forecast <- 17

#ESP
best_model_ESPPREM <- snaive(serviceseriesESPPREM, lambda = "auto") %>% forecast(h = months.forecast)
predictionsESPPREM <- predict(best_model_ESPPREM, newdata = future_production)

best_model_ESP19H <- auto.arima(serviceseriesESP19H, lambda = "auto") %>% forecast(h = months.forecast)
predictionsESP19H <- predict(best_model_ESP19H, newdata = future_production)

best_model_ESPECOM <- ets(serviceseriesESPECOM, lambda = "auto") %>% forecast(h = months.forecast)
predictionsESPECOM <- predict(best_model_ESPECOM, newdata = future_production)

best_model_ESPPPACK <- ets(serviceseriesESPPPACK, lambda = "auto") %>% forecast(h = months.forecast)
predictionsESPPPACK <- predict(best_model_ESPPPACK, newdata = future_production)

best_model_ESPOT <- auto.arima(serviceseriesESPOT, lambda = "auto") %>% forecast(h = months.forecast)
predictionsESPOT <- predict(best_model_ESPOT, newdata = future_production)

best_model_ESPI <- ets(serviceseriesESPI, lambda = "auto") %>% forecast(h = months.forecast)
predictionsESPI <- predict(best_model_ESPI, newdata = future_production)


#POR

best_model_PORPREM <- ets(serviceseriesPORPREM, lambda = "auto") %>% forecast(h = months.forecast)
predictionsPORPREM <- predict(best_model_PORPREM, newdata = future_production)

best_model_POR19H <- snaive(serviceseriesPOR19H, lambda = "auto") %>% forecast(h = months.forecast)
predictionsPOR19H <- predict(best_model_POR19H, newdata = future_production)

best_model_PORECOM <- auto.arima(serviceseriesPORECOM, lambda = "auto") %>% forecast(h = months.forecast)
predictionsPORECOM <- predict(best_model_PORECOM, newdata = future_production)

best_model_PORPPACK <- ets(serviceseriesPORPPACK, lambda = "auto") %>% forecast(h = months.forecast)
predictionsPORPPACK <- predict(best_model_PORPPACK, newdata = future_production)

best_model_POROT <- snaive(serviceseriesPOROT, lambda = "auto") %>% forecast(h = months.forecast)
predictionsPOROT <- predict(best_model_POROT, newdata = future_production)

best_model_PORI <- ets(serviceseriesPORI, lambda = "auto") %>% forecast(h = months.forecast)
predictionsPORI <- predict(best_model_PORI, newdata = future_production)


```

## Create forecast data_frame 

```{r}
#DATA FRAME PREDICTIONS
#ESP
df.predictions <- data.frame(date = as.Date(time(predictionsESPPREM$mean)), meanpred_ESPPREM = predictionsESPPREM$mean)
df.predictionsServices <- rbind(df.predictions)
rm(df.predictions)
df.predictions <- data.frame(date = as.Date(time(predictionsESP19H$mean)), meanpred_ESP19H = predictionsESP19H$mean)
df.predictionsServices <- merge(
           x = df.predictionsServices,
           y = df.predictions,
           by = "date",
           all.x = TRUE)
rm(df.predictions)
df.predictions <- data.frame(date = as.Date(time(predictionsESPECOM$mean)), meanpred_ESPECOM = predictionsESPECOM$mean)
df.predictionsServices <- merge(
           x = df.predictionsServices,
           y = df.predictions,
           by = "date",
           all.x = TRUE)
rm(df.predictions)
df.predictions <- data.frame(date = as.Date(time(predictionsESPPPACK$mean)), meanpred_ESPPACK = predictionsESPPPACK$mean)
df.predictionsServices <- merge(
           x = df.predictionsServices,
           y = df.predictions,
           by = "date",
           all.x = TRUE)
rm(df.predictions)
df.predictions <- data.frame(date = as.Date(time(predictionsESPOT$mean)), meanpred_ESPOT = predictionsESPOT$mean)
df.predictionsServices <- merge(
           x = df.predictionsServices,
           y = df.predictions,
           by = "date",
           all.x = TRUE)
rm(df.predictions)
df.predictions <- data.frame(date = as.Date(time(predictionsESPI$mean)), meanpred_ESPI = predictionsESPI$mean)
df.predictionsServices <- merge(
           x = df.predictionsServices,
           y = df.predictions,
           by = "date",
           all.x = TRUE)
rm(df.predictions)

#POR
df.predictions <- data.frame(date = as.Date(time(predictionsPORPREM$mean)), meanpred_PORPREM = predictionsPORPREM$mean)
df.predictionsServices <- merge(
           x = df.predictionsServices,
           y = df.predictions,
           by = "date",
           all.x = TRUE)
rm(df.predictions)

df.predictions <- data.frame(date = as.Date(time(predictionsPOR19H$mean)), meanpred_POR19H = predictionsPOR19H$mean)
df.predictionsServices <- merge(
           x = df.predictionsServices,
           y = df.predictions,
           by = "date",
           all.x = TRUE)
rm(df.predictions)
df.predictions <- data.frame(date = as.Date(time(predictionsPORECOM$mean)), meanpred_PORECOM = predictionsPORECOM$mean)
df.predictionsServices <- merge(
           x = df.predictionsServices,
           y = df.predictions,
           by = "date",
           all.x = TRUE)
rm(df.predictions)
df.predictions <- data.frame(date = as.Date(time(predictionsPORPPACK$mean)), meanpred_PORPPACK = predictionsPORPPACK$mean)
df.predictionsServices <- merge(
           x = df.predictionsServices,
           y = df.predictions,
           by = "date",
           all.x = TRUE)
rm(df.predictions)
df.predictions <- data.frame(date = as.Date(time(predictionsPOROT$mean)), meanpred_POROT = predictionsPOROT$mean)
df.predictionsServices <- merge(
           x = df.predictionsServices,
           y = df.predictions,
           by = "date",
           all.x = TRUE)
rm(df.predictions)
df.predictions <- data.frame(date = as.Date(time(predictionsPORI$mean)), meanpred_PORI = predictionsPORI$mean)
df.predictionsServices <- merge(
           x = df.predictionsServices,
           y = df.predictions,
           by = "date",
           all.x = TRUE)
rm(df.predictions)

head(df.predictionsServices)
```

#forecast of Type of services by month and country 

```{r}
#forecast in months 
df.predictionsServices<- merge(
           x = df.predictionsServices,
           y = df.lab[c("date","DLABESP","DLABPOR")],
           by = "date",
           all.x = TRUE,
           )


df.predictionsServices$DLABESP = as.numeric(df.predictionsServices$DLABESP)
df.predictionsServices$DLABPOR = as.numeric(df.predictionsServices$DLABPOR)

df.predictionsServices$FS_ESPPREM = df.predictionsServices$meanpred_ESPPREM * df.predictionsServices$DLABESP
df.predictionsServices$FS_ESP19H = df.predictionsServices$meanpred_ESP19H * df.predictionsServices$DLABESP
df.predictionsServices$FS_ESPECOM = df.predictionsServices$meanpred_ESPECOM * df.predictionsServices$DLABESP
df.predictionsServices$FS_ESPPACK = df.predictionsServices$meanpred_ESPPACK * df.predictionsServices$DLABESP
df.predictionsServices$FS_ESPOT = df.predictionsServices$meanpred_ESPOT * df.predictionsServices$DLABESP
df.predictionsServices$FS_ESPI = df.predictionsServices$meanpred_ESPI * df.predictionsServices$DLABESP

df.predictionsServices$FS_PORPREM = df.predictionsServices$meanpred_PORPREM * df.predictionsServices$DLABPOR
df.predictionsServices$FS_POR19H = df.predictionsServices$meanpred_POR19H * df.predictionsServices$DLABPOR
df.predictionsServices$FS_PORECOM = df.predictionsServices$meanpred_PORECOM * df.predictionsServices$DLABPOR
df.predictionsServices$FS_PORPPACK = df.predictionsServices$meanpred_PORPPACK * df.predictionsServices$DLABPOR
df.predictionsServices$FS_POROT = df.predictionsServices$meanpred_POROT * df.predictionsServices$DLABPOR
df.predictionsServices$FS_PORI = df.predictionsServices$meanpred_PORI * df.predictionsServices$DLABPOR

df.predictionsServices$FS_ESP = df.predictionsServices$FS_ESPPREM + 
                                df.predictionsServices$FS_ESP19H + 
                                df.predictionsServices$FS_ESPECOM +
                                df.predictionsServices$FS_ESPPACK + 
                                df.predictionsServices$FS_ESPOT + 
                                df.predictionsServices$FS_ESPI

df.predictionsServices$FS_POR = df.predictionsServices$FS_PORPREM + 
                                df.predictionsServices$FS_POR19H + 
                                df.predictionsServices$FS_PORECOM +
                                df.predictionsServices$FS_PORPPACK + 
                                df.predictionsServices$FS_POROT + 
                                df.predictionsServices$FS_PORI



head (df.predictionsServices)
write.csv(df.predictionsServices, file = "predictionsServices.csv")
write_excel_csv2(df.predictionsServices, file = "predictionsServicesEXCEL.csv")
```



Graphs:


```{r, fig.asp=0.4, fig.width=10}
autoplot(serviceseriesESP) +
  autolayer(best_model_ESP, series="ETS - ESP", alpha=0.9, size=1) +
  autolayer(serviceseriesESP, size=0.75, color=1, alpha=0.7)+
  

autoplot(serviceseriesPOR) +
  autolayer(best_model_POR, series="ETS - POR", alpha=0.9, size=1) +
  autolayer(serviceseriesPOR, size=0.75, color=1, alpha=0.7)
```


```{r, fig.asp=0.9, fig.width=10, ggtitle("SHIPMENTS FORECAST")}
autoplot(serviceseriesESPPREM) +
  autolayer(best_model_ESPPREM$mean, series="ESPPREM", color =1 , alpha=0.95, size=1) +
  autolayer(serviceseriesESPPREM, size=0.75, color=1, alpha=0.4)+
  autolayer(serviceseriesESP19H, size=0.75, color=2, alpha=0.4)+
  autolayer(best_model_ESP19H$mean, series="ES19H", color =2, alpha=0.95, size=1) +
  autolayer(serviceseriesESPECOM, size=0.75, color=3, alpha=0.4)+
  autolayer(best_model_ESPECOM$mean, series="ECOM", color=3, alpha=1,5, size=1) +
  autolayer(serviceseriesESPPPACK, size=0.75, color=4, alpha=0.4)+
  autolayer(best_model_ESPPPACK$mean, series="PPACK", color =4, alpha=0.95, size=1) + 
  autolayer(serviceseriesESPOT, size=0.75, color=5, alpha=0.4)+
  autolayer(best_model_ESPOT$mean, series="OT", color = 5, alpha=0.95, size=1) +
  autolayer(serviceseriesESPI, size=0.75, color=6, alpha=0.4)+
  autolayer(best_model_ESPI$mean, series="I", color =6, alpha=0.95, size=1)
  
```


```{r, fig.asp=0.9, fig.width=10}
autoplot(serviceseriesPORPREM) +
  autolayer(best_model_PORPREM$mean, series = "ESPPREM", color =1 , alpha=0.95, size=1) +
  autolayer(serviceseriesPORPREM, size=0.75, color=1, alpha=0.4)+
  autolayer(serviceseriesPOR19H, size=0.75, color=2, alpha=0.4)+
  autolayer(best_model_POR19H$mean, series="ES19H", color =2, alpha=0.95, size=1) +
  autolayer(serviceseriesPORECOM, size=0.75, color=3, alpha=0.4)+
  autolayer(best_model_PORECOM$mean, series="ECOM", color=3, alpha=1,5, size=1) +
  autolayer(serviceseriesPORPPACK, size=0.75, color=4, alpha=0.4)+
  autolayer(best_model_PORPPACK$mean, series="PPACK", color =4, alpha=0.95, size=1) + 
  autolayer(serviceseriesPOROT, size=0.75, color=5, alpha=0.4)+
  autolayer(best_model_POROT$mean, series="OT", color = 5, alpha=0.95, size=1) +
  autolayer(serviceseriesPORI, size=0.75, color=6, alpha=0.4)+
  autolayer(best_model_PORI$mean, series="I", color =6, alpha=0.95, size=1)
  
```


```{r}
#REAL DATA 
#ESP

df.realdata <- select(df.tmservicesESP19H, Date, total_sum)
colnames(df.realdata)[colnames(df.realdata) == "total_sum"] <- "ESP19H"
df.realdata<- merge(
           x = df.realdata,
           y = df.tmservicesESPPREM[c("Date","total_sum")],
           by = "Date",
           all.x = TRUE,
           )
colnames(df.realdata)[colnames(df.realdata) == "total_sum"] <- "ESPPREM"
df.realdata<- merge(
           x = df.realdata,
           y = df.tmservicesESPECOM[c("Date","total_sum")],
           by = "Date",
           all.x = TRUE,
           )
colnames(df.realdata)[colnames(df.realdata) == "total_sum"] <- "ESPECOM"
df.realdata<- merge(
           x = df.realdata,
           y = df.tmservicesESPPPACK[c("Date","total_sum")],
           by = "Date",
           all.x = TRUE,
           )
colnames(df.realdata)[colnames(df.realdata) == "total_sum"] <- "ESPPPACK"
df.realdata<- merge(
           x = df.realdata,
           y = df.tmservicesESPOT[c("Date","total_sum")],
           by = "Date",
           all.x = TRUE,
           )
colnames(df.realdata)[colnames(df.realdata) == "total_sum"] <- "ESPOT"
df.realdata<- merge(
           x = df.realdata,
           y = df.tmservicesESPI[c("Date","total_sum")],
           by = "Date",
           all.x = TRUE,
           )
colnames(df.realdata)[colnames(df.realdata) == "total_sum"] <- "ESPI"




df.realdata<- merge(
           x = df.realdata,
           y = df.tmservicesPOR19H[c("Date","total_sum")],
           by = "Date",
           all.x = TRUE,
           )
colnames(df.realdata)[colnames(df.realdata) == "total_sum"] <- "POR19H"
df.realdata<- merge(
           x = df.realdata,
           y = df.tmservicesPORPREM[c("Date","total_sum")],
           by = "Date",
           all.x = TRUE,
           )
colnames(df.realdata)[colnames(df.realdata) == "total_sum"] <- "PORPREM"
df.realdata<- merge(
           x = df.realdata,
           y = df.tmservicesPORECOM[c("Date","total_sum")],
           by = "Date",
           all.x = TRUE,
           )
colnames(df.realdata)[colnames(df.realdata) == "total_sum"] <- "PORECOM"
df.realdata<- merge(
           x = df.realdata,
           y = df.tmservicesPORPPACK[c("Date","total_sum")],
           by = "Date",
           all.x = TRUE,
           )
colnames(df.realdata)[colnames(df.realdata) == "total_sum"] <- "PORPPACK"
df.realdata<- merge(
           x = df.realdata,
           y = df.tmservicesPOROT[c("Date","total_sum")],
           by = "Date",
           all.x = TRUE,
           )
colnames(df.realdata)[colnames(df.realdata) == "total_sum"] <- "POROT"
df.realdata<- merge(
           x = df.realdata,
           y = df.tmservicesPORI[c("Date","total_sum")],
           by = "Date",
           all.x = TRUE,
           )
colnames(df.realdata)[colnames(df.realdata) == "total_sum"] <- "PORI"

write.csv(df.realdata, file = "rdataServices.csv")
write_excel_csv2(df.realdata, file = "rdataEXCEL.csv")


head(df.realdata)
```

